The Castro AMR Simulation Code: Current and Future Developments

### 2019-10-01 astronum_2019_Castro/astronum-castro-2019.tex
more progress

The \castro\ astrophysical simulation code~\cite{castro} is designed
for modeling problems in nuclear astrophysics, with the ability to
accurately capture the interplay between hydrodynamics, reactions,
gravity, and radiation in stars with complex equations of state.
Since \castro\ was first development, there have been a number of
enhancements to the code base, expanding its applicability to a new
range of scientific problems.

\castro\ has been applied to models of Type Ia supernovae,
core-collapse supernovae, pair-instability supernova, and most
recently X-ray bursts.  A common challenge in modeling these events is
the range of length and timescales involved.

>>>>

The \castro\ astrophysical simulation code~\cite{castro} is designed
for modeling problems in nuclear astrophysics, with the ability to
accurately capture the interplay between hydrodynamics, reactions,
gravity, and radiation in stars with complex equations of state.
Since \castro\ was first developed, there have been a number of
enhancements to the code base, expanding its applicability to a new
range of scientific problems.  The most active development presently
focuses on new methods of time integration, with better coupling of
physical processes, and GPU performance.  Here we discuss some of
these features.

\castro\ has been applied to models of Type Ia supernovae,
core-collapse supernovae, pair-instability supernovae, exoplanet
atmospheres, and most recently X-ray bursts (see, e.g.,
\cite{castro-ccsne,castro-pairinstability,polin:2019,wdmergerI} for
some example science applications).  A common challenge in modeling
these events is the range of length and timescales involved.
